%\newpage

\cvsection {\faMicrophone\space Abstracts}

%\cvsubsection{Invited Talks} \vspace{-2mm}

%\begin{cvpubs}

%\cvpub
%{\hspace{-1cm} \textit{Total: 14}}
%{}

%\cvpub
%{Dynamic secondary metabolism in a model rhizosphere community. International Symposium on the Biology of Actinomycetes. Toronto, ON. Jun 20, 2022.}
%{1}

%\cvpub
%{Microbial secondary metabolism: from evolutionary genomics to
%community ecology. Latin American Workshop on Genome Mining of Natural Products. Guanajuato, Mexico. Jun 15, 2022.}
%{2}

%\cvpub
%{Dynamic secondary metabolism in a model rhizosphere community. Synthetic Biology for Natural Products Conference. Cancun, Mexico. May 18, 2022.}
%{3}

%\cvpub
%{``Evolution of antibiotic biosynthesis as a framework for drug discovery." Biotechnology Institute Seminar Series. University of Minnesota. St. Paul, MN (remote). Dec 17, 2020.}
%{4}

%\cvpub
%{``Evolution of antibiotic biosynthesis as a framework for drug discovery." Whitney Laboratory for Marine Bioscience Seminar Series. University of Florida. Gainesville, FL (remote). Sep 25, 2020.}
%{5}

%\cvpub
%{``The Earth’s bounty: antibiotic discovery from soil." Gairdner Symposium, McMaster University. Hamilton, ON. Nov 15, 2019.}
%{6}

%\cvpub
%{``Drugs from bugs of bugs: a novel source for antimicrobials." American Society for Microbiology Microbe. San Francisco, CA. Jun 21, 2019.}
%{7}

%\cvpub
%{``Mining microbiomes for antimicrobials." Synthetic Biology for Natural Products Conference. Puerto Vallarta, Mexico. Jun 02, 2019.}
%{8}

%\cvpub
%{``Drugs from bugs of bugs: microbiomes as a source of new antibiotics." Wisconsin Institute for Discovery. Madison, WI. Jan 24, 2019.}
%{9}

%\cvpub
%{``Drugs \& bugs of bugs: insect microbiomes as a source of new antibiotics."  McMaster University. Hamilton, ON. Jun 21, 2018.}
%{10}

%%\cvpub
%{``Host-associated microbes as a source of new antimicrobials." Natural Product Discovery \& Development in the Genomic Era, Society for Industrial Microbiology \& Biotechnology. Clearwater Beach, FL. Jan 22, 2018.}
%{11}

%\cvpub
%{``Natural natural products: Leveraging chemical ecology in the search for new drugs." Evolution Seminar Series, JF Crow Institute for the Study of Evolution. Madison, WI. Oct 26, 2017.}
%{12}

%\cvpub
%{``Computational insights into the diverse nonribosomal peptide chemistry of Actinobacteria." Synthetic Biology for Natural Products Conference. Cancun, Mexico. Mar 6, 2017. \linebreak \textbf{[\textit{\colorhref{https://doi.org/10.1021/acssynbio.7b00132}{Highlighted in ACS Synthetic Biology}}]}}
%{13}

%\cvpub
%{``Darwinian drug discovery: Chemical ecology at fine and coarse %evolutionary scales." International Chemical Biology Society Annual Conference. Madison, WI. Oct 24, 2016. \linebreak \textbf{[\textit{\colorhref{https://doi.org/10.1021/acschembio.7b00205}{Highlighted in ACS Chemical Biology}}]}}
%{14}

%\end{cvpubs}

%--------------------------------

%\cvsubsection{Internal Seminars} \vspace{-2mm}

%\begin{cvpubs} 

%\cvpub
%{\hspace{-1cm} \textit{Total: 6}}
%{}

%\cvpub
%{``Using antiSMASH as both an antibiotic discovery \& teaching tool." Tiny Earth Symposium 2020, UW-Madison. Jun 12, 2020.}
%{1}

%\cvpub
%{``Tiny Earth Chemistry Hub: the next stop for your samples." Tiny Earth Symposium 2019, UW-Madison. Jul 10, 2019.}
%{2}

%\cvpub
%{``Drugs \& bugs of bugs: Insect microbiomes as a source of new antibiotics." Genetics Colloquium, UW-Madison. Aug 8, 2018.}
%{3}

%\end{cvpubs}

%--------------------------------

\cvsubsection{Abstracts} \vspace{-2mm}

\begin{cvpubs}

%\cvpub
%{\hspace{-1cm} \textit{Total: 32; Listed below: 2017--present}}
%{\hspace{-1cm} \textit{Listed below: 2017--present}}
%{}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}},, MG Chevrette. ``GATOR-GC Identifies a Rich Landscape of Overlooked Biosynthetic Gene Clusters (BGCs)." Presented at: 10th in the series of John Innes – Rudjer Bošković Summer Schools on Applied Molecular Microbiology. ; Dubrovnik, Croatia; Sep 12, 2024.}
{1}

\cvpub
{M Saldanha, \textbf{\underline{JDD Cediel-Becerra}}, S Manning, F Barona-Gomez, MG Chevrette. ``A global analysis of Bacterial Genomes Links Secondary Metabolism and Antibiotic Resistance." Presented at: Society for Industrial Microbiology and Biotechnology (SIMB) Annual Meeting; Minneapolis, MN; Aug 02, 2024.}
{2}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, A Cumsille, Vd Crecy-Lagard, MG Chevrette. ``Targeted Genomic Searches to Mine Gene Cluster Evolution in Host-Associated Microbes." Presented at: 9th Conference on Beneficial Microbes; Madison, WI; July 21, 2024.}
{3}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, Vd Crecy-Lagard, MG Chevrette. ``GATOR-GC: Genomic Assessment Tool for Orthologous Regions and Gene Clusters ." Presented at: UF Drug Discovery Symposium; Gainesville, FL; April 15, 2024.}
{4}

\cvpub
{M Saldanha, \textbf{\underline{JDD Cediel-Becerra}}, S Manning, MG Chevrette. ``A global analysis of Bacterial Genomes Links Secondary Metabolism and Antibiotic Resistance." Presented at: EPI Research Day; Gainesville, FL; Feb 26, 2024}
{5}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, Vd Crecy-Lagard, MG Chevrette. ``7-Deazapurine-derived natural products: An Incredible Potential Source for Drug Discovery." Presented at: Genetics and Genomics Annual Symposium; Gainesville, FL; Nov 16, 2023.}
{6}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, Vd Crecy-Lagard, MG Chevrette. ``Genome Mining Strategies for Non-Canonical Biosynthetic Gene Clusters." Presented at: Microbiology and Cell Science Annual Symposium; Gainesville, FL; Aug 16, 2023.}
{7}

\cvpub
{MA Gatmaitan, \textbf{\underline{JDD Cediel-Becerra}}, Julia Charske, Mark Ou, Marc G. Chevrette. ``Cockroach-associated Bacteria and Their Antimicrobial Activity." Presented at: American Society of Pharmacognosy (ASP) Annual Meeting; Rockville, MD; Jul 26, 2023}
{8}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, Vd Crecy-Lagard, MG Chevrette. ``Deazaguanine Gene Clusters in \textit{Streptomyces} Reveal Putative Nucleoside-Like Natural Products." Presented at: Society for Industrial Microbiology and Biotechnology (SIMB) Annual Meeting; Minneapolis, MN; Aug 02, 2023.}
{9}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, Vd Crecy-Lagard, MG Chevrette. ``PreQ0 Gene Clusters in \textit{Streptomyces} Reveal an Unexplored Biosynthetic Reservoir." Presented at: American Society of Pharmacognosy (ASP) Annual Meeting; Rockville, MD; Jul 26, 2023.}
{10}
\end{cvpubs} \begin{cvpubs}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, JA Suescun Sepulveda, JL Fuentes. ``Photoprotective and Antigenotoxic Properties of \textit{Serratia marcescens} Indigenous Strains from Eastern Cordillera of Colombia." Presented at: 19th Congress of the European Society for Photobiology (ESP); WWW and Salzburg, Austria; Aug 30, 2021.}
{11}




%\cvpub
%{\underline{\textbf{MG Chevrette}}, D Acharya, A Hurley, M Beebe, M Garavito, S Miller, J Handelsman. ``Tiny Earth Chemistry Hub: From soil to antibiotics." Presented at: Tiny Earth Symposium; Madison, WI; Jul 10, 2019.}
%{4}


\end{cvpubs}